The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-01 paper/Analisis.tex
New ideas in discussion + one paragraph

... Comparison with Verhamme et al. results on the rotation (Viewing angle)

@@

% BUSCAR asimetrias en observaciones, KUlas, YAMADA  off-center emission

>>>>

Following the classification of $Ly\alpha$ profiles made for (Kulas et al, put reference) 
we divide our results in $3$ different groups. Group I represents profiles in which the flux in the red side 
is stronger that in the blue part, while Group II represents profiles in which the blue side
is the stronger. Group III represents single peaked profiles while Group IV represents multipeaked  
profiles.

Group I profiles may be explained in our model when off-center emission is present and the location 
of this photons emission is stronger in the , while Group II profiles correspond to emissions in the ..

Group III profiles are better represented by galaxies rotating at $V > 100 kms^{-1}$\\
... Comparison with Verhamme et al. results on the rotation (Viewing angle)

@@

% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail observaciones, Kulas, YAMADA  off-center emission
